sims

### 2025-06-14 manuscript/ResponseReview1.Rmd

---
title: "Review 1: Author responses"
author: "Panis & Ramsey"
date: "12.06.2025"
output: 
  pdf_document:
      keep_tex: true
header-includes:
  - \usepackage{framed}
  - \usepackage{xcolor}
  - \let\oldquote\quote
  - \let\endoldquote\endquote
  - \renewenvironment{quote}{\begin{leftbar}}{\end{leftbar}}
---

```{r setup, include=FALSE}
# By default, the code chunks are hidden for brevity. Set the echo argument to TRUE for blocks you want to share the code in the output for. 
knitr::opts_chunk$set(echo = F)
```

```{r packages and data, include=F }

```

# Editor

> 15-Mar-2025
>
> Dear Dr. Panis:
>
> Thank you for submitting your Tutorial (AMPPS-24-0232) entitled "Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows" to Advances in Methods and Practices in Psychological Science (AMPPS). I have now received input from three experts in the field, and you will find the reviews below this message and attached. As you will see, all three reviewers believe your paper can make a strong contribution to the literature. Prior to considering the reviewers' input, I read your paper to form an independent opinion. I share the positive sentiments about this work and invite you to revise and resubmit your manuscript for further consideration at AMPPS.

> The reviews are through and thoughtful, and I will not reiterate all the details here. For my part, I would like your revision to focus on accessibility. Your paper is a bit challenging-- it's long and a little tough to get through. What can make it easier for less familiar readers? Perhaps more of a basic set up earlier? A glossary defining specific terms (e.g., what is an event? how is it defines? censoring? hazards vs. survival curves, conditional probabilities, etc.)? Also, clarify when readers need to shift from frequentist to Bayesian model... and why? The main consideration here is that wish to make the paper much more accessible-- from start to finish-- for readers who are novices and entirely unfamiliar with this area. This can be done any number of ways, and R3 also includes some suggestions for making these reviews. 
I encourage you to have the revised paper read and pre-reviewed by colleagues who are novices in this area with the explicit goal of making the paper accessible to them-- this will help you hit the more for our broad readership.

> If you choose to submit a revision, please include include a letter detailing your point-by-point responses to each reviewer comment and indicating how you changed the manuscript to address them. The revised manuscript may undergo further peer review. We ask that you submit your revision within three months. Please let us know if you will not be able to meet this deadline.

> To submit your revision, log into http://mc.manuscriptcentral.com/ampps and enter your Author Center, where you will find your manuscript title listed under "Manuscripts with Decisions." Under "Actions," click on "Create a Revision." Your manuscript number has been appended to denote a revision.

> IMPORTANT: Your original files are available to you when you upload your revised manuscript. Please delete any redundant or outdated files before completing the submission.

> Once again, thank you for submitting your manuscript to AMPPS and I look forward to receiving your revision.

> Sincerely,

> David A. Sbarra, Ph.D.
> Editor, Advances in Methods and Practices in Psychological Science

We tried to focus on accessibility in the revision of our Tutorial AMPPS-24-0232.

# Reviewer: 1

> Comments to the Author
> It was a pleasure to review this manuscript as someone who has spent years applying survival analysis methods to psychological data. This is an ambitious manuscript and I believe it achieves its goals. The key contributions of this manuscript from my perspective are the creation of custom functions for data wrangling, and the section on planning studies/simulations for power analysis (of course, in addition to the introduction to this category of methods and the practical tutorials provided. I have some comments on this work that I believe could strengthen this manuscript’s contribution.

> General comments:

> The Introduction is really nicely framed in terms of providing compelling information for why this class of statistical models would be useful in some specific areas of psychology (i.e., reaction time data). Given that there are already a couple of tutorial-types of articles introducing specific applications of survival analysis in developmental psychology (references below, both regarding the use of these methods for behavioural observations of emotional expressions in a multilevel framework for recurring events), it would be helpful to further frame the unique contribution that this work adds. The authors may also consider further emphasizing the specific theoretical contributions that using these methods may lead to in the areas of reaction time data etc.

Response: In the revised ms. We added the following section: In this tutorial we provide code to implement discrete-time hazard models in a Bayesian framework, with a focus on cognitive experimental psychology.

> Lougheed, J. P., Benson, L., Ram, N., & Cole, P. M. (2019). Multilevel survival analysis: Studying the timing of children’s recurring behaviors. Developmental Psychology, 55(1), 53–65. https://doi.org/10.1037/dev0000619

> Stoolmiller, M. (2016). An introduction to using multivariate multilevel survival analysis to study coercive family process. In T. J. Dishion & J. J. Snyder (Eds.), The Oxford handbook of coercive relationship dynamics (pp. 363–378). Oxford University Press.

> Stoolmiller, M., & Snyder, J. (2006). Modeling heterogeneity in social interaction processes using multilevel survival analysis. Psychological Methods, 11(2), 164–177. https://doi.org/10.1037/1082-989X.11.2.164

Response: We added these references to the ms.

> Similarly, it would be helpful to make it clear that this manuscript pertains to estimating single-event occurrences rather than recurring events (which are described in the Lougheed and Stoolmiller tutorials mentioned above)

Response: On page x of the revised ms., we mention that we estimate single-event occurrences that are repeatedly measured in each participant.

> Specific comments:

> The authors use several different terms to refer to time-to-event models throughout the manuscript. The title refers to EHA, and the running head refers to Hazard analysis. Survival analysis is also a common term in Psychology (see tutorials by Lougheed et al., 2019, and Stoolmiller & Snyder, 2006). Disambiguating the various terms early in the manuscript and then constantly using one term throughout the manuscript would be helpful.

Response: We disambiguate the various term early in the revised ms. (page x).

> Page 5: it would be helpful to refer to the same time unit in reference to Figure 1, which shows time bins along the x-axis but the examples discussed in the manuscript refer to units of milliseconds.

Response: We refer to the same time unit in Figure 1 and the text.

> Page 7: The authors state that they are not aware of EHA tutorials for psychological time to event data. Previoulsy mentioned tutorial articles by Lougheed and Stoolmiller could be mentioned here— these are demonstrating applications to behavioural observation data within psychology.

Response: We added these 3 references to the revised ms.

> Page 8: I’m curious about the decision to focus on discrete time rather than continuous time models. It would help the reader to explain the decision either way, or refer the reader to Lougheed et al., 2019 who discuss this distinction and choices that researchers may make regarding how to handle decisions around time given data formats. I don’t work with reaction time data, but it seems to me that many experiments in this area would collect data in continuous time intervals, and it’s not clear to me what the benefit of discretizing into time bins is. Now that I’ve read the entire manuscript, I see that some information is presented on this on Page 50, but it would be helpful to make this information known to the reader earlier in the manuscript.

Response: We address the issue of treating time as discrete or continuous on page x of the revised ms.

> Page 8-9, excellent and accessible explanations of the survival function in the discrete time framework.

Response:

> Page 11: In my experience, researchers in psychology are generally not familiar with the concept of right censored data. This term is first used on page 11 with no explanation— a brief, even parenthetical, definition would be helpful. For example, the parenthetical definition on page 48 could be provided on page 11.

Response: We define right-censoring on page x of the revised ms.

> Taken together, this is an excellent manuscript with the potential to further bring survival analysis methods into Psychology, where time-to-event and right-censored cases abound, yet very few people seem to consider these issues.

# Reviewer: 2

> Comments to the Author
> Please see attached file for comments.

> Reviewer report for AMPPS-24-0232: “Event History Analysis for psychological time-to-
event data: A tutorial in R with examples in Bayesian and frequentist workflows”
Summary: The authors present a tutorial paper on the analysis of discrete time-to-event
outcomes. They motivate their tutorials with a description of psychological experiments
that produce time-to-event data and explain how simply summarizing event-time
outcomes using means results in a loss of potentially important information. They then
explain how more information can be gleaned from event-time data if they are
summarized using event history analysis methods. They focus specifically on the
analysis of discrete time-to-event outcomes. They provide code for conducting the
analyses in the tutorials on their Github. Overall, I like the idea of this paper and
strongly agree that using methods appropriate for analyzing time-to-event data, rather
than simply summarizing event-time outcomes using means, is very important and
currently underused. While I like the premise of the paper and think that such a paper
could be a valuable contribution to the literature, I do think the paper has room for
improvement in a number of areas (see comments below). The writing is approachable
(which is advantageous for a tutorial paper) but some text in the paper was repetitive
and could be a bit more polished; additional editing with a focus on clarity and brevity
would be beneficial.

Response: We removed repetitive text, and try to focus on clarity and brevity in the revised ms.

> Major comments:
1. Some discussion on the choice of bin width is needed. Since all of the example
time-to-event data is collected in continuous time, the analyst must discretize it
by defining bins. Defining bins is a key step in the analysis pipeline and so
should not be overlooked. It seems like results—and potentially conclusions
drawn—may depend on the choice of bin width. What factors should the analyst
consider when defining the width of the bins? Does the number of bins matter?
Or is the number of events per bin important? What about other factors? Should
analysts (or potentially these authors too) consider multiple bin widths when
conducting an analysis? An example comparing results when bin width varies
could be both interesting and informative.

Response: We discuss the issue of defining bins on page x of the revised ms.

> 2. In the discussion, the authors mention that they choose to present a tutorial on
discrete time analysis methods because they believe these are easier to
understand. My personal impression is that awareness of continuous time
analysis methods is slightly higher and so researchers may be more familiar with
methods such as Cox models, even if they have not used them themselves;
however, this could vary by specific sub-field. I agree with the authors that the
interpretation of the hazard is easier in the discrete time setting than in the
continuous time setting, but I do think that the distinction between the
interpretation of the hazard in continuous vs discrete time should be discussed in
the introduction. When I first read the introduction, I was confused as to why the
focus was on discrete time methods, when the outcome measures collected in
the motivating data were collected in continuous time. I would suggest either of
the following: (a) provide concrete examples of when truly discrete timeoutcomes are collected to strengthen the motivation of the paper and justification
for use of discrete time analysis methods or (b) keep the motivating examples as-
is and include a short comparison of discrete vs. continuous time analysis
methods to help explain your reasoning for choosing to focus on discrete time
analysis methods.

Response: We include a short comparison of both methods on page x of the revised ms.

> 3. Censoring is an important part of time-to-event data and so more description of
censoring—and how it is (not) accounted for in “orthodox” analysis methods vs.
discrete time-to-event analysis methods would be useful, beyond the already-
included mention of censoring in Section 5.3.

Response: We define (right-)censoring on page x of the revised ms.

> 4. Section 1.2 is a bit long. Please shorten this section to improve the clarity of the
text and reduce redundancy. There is also overlap between text in Section 1.2
and the start of Section 4.

Response: We shortened this section and removed the overlap.

> 5. Section 2.3.2. I like the idea of making a connection with experimental design,
but am having trouble seeing how the discussion in this section is specific to EHA
and how these comments do not apply also to the “orthodox method”. I think this
section could be improved by providing more specific distinctions between
experimental design implications for EHA vs. the “orthodox method”.

Response: We added the following section on page x of the revised ms.: …

> 6. Line 517: What are model weights? Please explain briefly for the reader,
including how the interpretation differs for loo and waic. Also, in the provided
reference (Kruz 2023a), I was only able to find a discussion of dWAIC, rather
than WAIC, so could you please include a definition of or reference for dWAIC in
your context? Lastly, when reporting the model weights in the example in the
text, I’d suggest including more than 2 digits so that it is clear if the reported
weights are actually 0 and 1 or if rounding has just made them appear so.

Response: We explain model weights on page x, include a reference for dWAIC, and report the weights with 3 digits.

> 7. Tutorials 3a and 3b: Rather than simply stating that the frequentist models did
not converge and resulted in singular fits, it would be helpful to provide more
discussion. Do you have an idea why the models did not converge? Since this
is a tutorial paper, more explanation is needed. These frequentist examples
don’t add much to the paper in their current form, so I’d either suggest either (a)
providing some suggestions to the reader of alternative approaches or specific
strategies that could be used to define a model that will converge or (b) removing
these examples from the main text and directing the reader to the supplement
instead.

Response: We removed the frequentist examples from the main text into the supplementary material.

> Minor comments:
> 1. Is “mean-average comparison” standard terminology? This phrase seems
redundant to me, since means and averages are the same thing.

Response: We removed this term.

> 2. Figure 1: In the caption, please state what the small error bars in the inset plots
are showing.

Response:

> 3. Please consider updating all plots so that they are understandable when viewed
in black and white. In addition to using different colors, I’d suggest distinguishing
the conditions using shapes (e.g., circles vs. triangles) and different line type
(e.g., solid vs. dashed lines).

Response:

> 4. Figure 2 caption:a. Please provide a reference for the statement beginning, “Because the
survival function…”.

Response:

> b. I am confused by the sentence beginning: “For example, the high hazard
of …”. Could you please provide some additional explanation or a
reference for more details on this interpretation?

Response:

> 5. Lines 156-166: Generally, survival probabilities are described as probabilities of
remaining event-free up until a certain point, rather than the probability of an
event occurring in the future. Some clarity in wording could be used here.

Response:

> 6. Please confirm that you have defined all acronyms, abbreviations, and functions
at their first use in the text. E.g., please define WAIC, LOO, P(t), ca(t), SOA, CrI,
among others.

Response: We define all acronyms on their first mention in the revised ms.

> 7. Section 3.1 could be condensed in the main paper (additional details could be
included in the supplementary material if important). Also, please double check
your definition of functional programming.

Response:

> 8. Table 2: It could be helpful to show an example of a trial where an event never
occurs, to help the reader connect what is written in the text (line 325-327) to
what appears in the table.

Response:

> 9. Figure 4: Why is there no bin 40?

Response:

> 10. Line 423: The phrase “early responses” is confusing as it implies temporal
ordering of the responses (i.e., early vs. late trials). I’d suggest using “fast
response” or “rapid responses”, or some other phrase along those lines.

Response:

> 11. Is the discussion of reference and index coding (lines 457 – 464) needed? In the
introduction, the authors state that knowledge of regression is assumed so I am
not sure this is necessary to include, but I defer to the authors’ judgment.

Response: Index coding is not used a lot in experimental psychology so we included a short discussion.

> 12. Figure 6: I only see one width of credible interval for each line on this plot—
please clarify if you are plotting 80% or 95% credible intervals.

Response:

> 13. Line 536: To me, “subject-specific” and “marginal” mean the opposite things.
That is, subject-specific is an effect that is conditional on an individual while a
“marginal” effect has been marginalized/averaged over individuals. Could you
please clarify your use of these terms here?

Response:

> 14. Lines 584-587: Since this is a tutorial paper, I’d suggest including explanations
for why you make changes (a), (b), and (c).

Response:

> 15. Line 659: What is a “fully varying effects structure”? Please define/explain.

Response:

> 16. Line 832-833: Please provide a reference for the statement, “However, they
require much more data…”.

Response:

> 17. Github code: Instruction 2 of the README states “open the
reproducible_workflow.Rproj” – I can’t find this R project, should it be the
“Tutorial_EHA.Rproj” instead?

Response:

# Reviewer: 3

> Comments to the Author
This tutorial guides readers through how to wrangle cognitive reaction time data and address research questions pertaining to temporal dynamics of cognition using event history analysis (EHA) and speed/accuracy tradeoff analysis (SAT). Models are illustrated for hazard functions, and conditional accuracy functions. A nice feature of this study is that each model is presented in both the Bayesian and frequentist frameworks. Having both frameworks provides side-by-side comparisons such as when the Bayesian framework might be preferred (e.g., when models do not converge in the Frequentist framework, which is common when modeling multilevel data). The tutorial also includes a section on simulation and power analysis for planning experiments. I believe this tutorial could eventually be a useful contribution to fellow psychological scientists. However, in its current state, it was difficult to follow/ make my way through (despite existing expertise in EHA), and also difficult to understand what the main contributions were above and beyond existing works. Additionally, it was not clear why the discrete time framework was chosen. The temporal granularity of reaction time data seems like it would be better suited for a continuous time framework. Altogether, the tutorial covers important concepts, but it would benefit from greater accuracy and clearer definitions of key terms. Carefully removing redundancies, getting to the tutorial section much quicker (currently not until pg. 17), and being more precise with explanations of technical jargon would enhance its clarity and accuracy.

Response: We discuss the main contributions above and beyond existing works on page x of the revised ms. We address the issue of treating time as discrete or continuous on page x of the revised ms. We removed redundancies  and included more precise explanations of technical jargon.

> <b>Code for the tutorials:</b> I went to the github page and found a folder for each of the 4 tutorials, which included sub-folders for data, figures, and tables. It took a minute for me to realize that the actual R code for each tutorial was in the main folder, not within each sub-folder. This may also be confusing to readers. Additionally, each of the 4 tutorials, along with their sub-tutorials are provided in separate .Rmd files. There were several download steps needed to get all the information. To me, this made the user experience tedious, and made the tutorials seem disjointed from one another. The authors might consider a more comprehensive single Rmd file that is neatly organized with an interactive table of contents (in the knitted html file). To me, this would make the experience much more enjoyable and useful for readers. Given that this is a tutorial, it would also be nice if the the RMarkdowns were somewhat more standalone e.g., by including a brief description of what a life table is and how to interpret the plot.

Response: We explain the location of the files in the README file. We included a brief description of a life table and how to interpret the plot in the R Mardown tutorial files. A single download step is possible by either cloning the project, or downloading the ZIP file.

> <b>Contribution of this tutorial:</b>
It wasn’t clear to me as a reader what the unique contribution is for this tutorial and what gaps in the literature it fills beyond existing texts and tutorials. For example, is this a tutorial that is meant to specifically focus on experimental psychology cognitive task data – and that this type of data has special characteristics/associated research questions that necessitate their own stand-alone tutorial? If so, it may be helpful to give more detail on what these specific characteristics tend to be that may make it different from the many other types of psychology data. Or, is this a tutorial on discrete time survival analysis that is meant to be broadly applicable to psychological scientists, and the cognitive reaction time data is just for illustrative purposes. If so, then much less emphasis should be placed on the specific data type and more emphasis should be placed more broadly on types of psychological data/ research questions this method could be applied to. I think the distinction makes a big difference in the entire framing of the tutorial, and choosing one or the other will make the tutorial content much easier for readers to absorb.

### 2025-06-14 sims/sims.Rmd
Add code for Figure 1 in revision1

```{r}
data_n10 <- sim_haz(subj_n = 10, rep_n = 200)
data_n20 <- sim_haz(subj_n = 20, rep_n = 200)
```

@@

ggsave("sims/figures/haz_acc_single.jpeg",
       width = 7, height = 6, dpi=800)

@@

>>>>

```{r}
data_n10 <- sim_haz(subj_n = 10, rep_n = 200)
head(data_n10)

data_n20 <- sim_haz(subj_n = 20, rep_n = 200)
```

@@

#ggsave("sims/figures/haz_acc_single.jpeg",
#       width = 7, height = 6, dpi=800)

@@

# section 13: REVISION 1: Create New Figure 1

In Figure 1 of the revision, we want to display for 1 subject the hazard and ca functions for 2 conditions, and the corresponding four means.

Steps:

## 1. Generate discrete time-to-event data for 1 subject, 2 conditions, 100 trials, and 10 time bins;

Adjust function:

```{r}
sim_haz <- function(subj_n = 10, rep_n = 200, bin_n = 10, cond_n = 2,  # these can be changed when calling the f
               hazard_cond1 = c(0, 0.02, 0.08, 0.19, 0.42, 0.52, 0.43, 0.41, 0.41, 0.39),
               hazard_cond2 = hazard_cond1*c(1, 1, 1, 1, .5, 0.3, 0.7, 1, 1,1),
               hazard = c(hazard_cond1, hazard_cond2),   # 
                ... # helps the function work with pmap() below
                ) {

  # set up data structure
  data <- add_random(subj = subj_n, rep = rep_n) %>% 
  add_within("subj", condition = c("cond1", "cond2")) %>%
  add_contrast("condition", "treatment", add_cols = TRUE, colnames = c("contrast")) %>%
  add_within("subj", bin = 1:bin_n) %>% 
  mutate(hazf = rep(hazard, length.out = subj_n * rep_n * bin_n * cond_n),
         event = rbinom(n(), 1, hazf)) %>% 
  group_by(subj, rep, condition) %>%
  mutate(cumsum = cumsum(event),
         outcomel = event==1 & cumsum(event) < 2,
         outcomen = if_else(event==1 & cumsum(event) == 1, 1,
                     if_else(cumsum(event) >= 1, NA, 0))) %>% 
  drop_na(outcomen) %>% 
  ungroup()
}
```

Generate data:

n_trials=200
## apply function sim_haz
data_fig1_hazard <- sim_haz(subj_n = 1, rep_n = n_trials) %>%
               mutate(subj = factor(subj),
                      trial = as.integer(str_sub(rep, start=4, end=6)),
                      acc = ifelse(bin<5 & condition=="cond2",0,1),
                      acc = ifelse(bin==5 & trial < 100,0,acc)) %>%
               select(-c("contrast","cumsum","outcomel","outcomen","rep"))

head(data_fig1_hazard, n=20)
summary(data_fig1_hazard)
```

Set up life table for generated data:

```{r}
lifetable_fig1 <- data_fig1_hazard %>%
    mutate(event = str_c("event", event)) %>%
    group_by(condition,bin) %>% 
    count(event) %>% 
    ungroup() %>% 
    pivot_wider(names_from = event,
                values_from = n) %>% 
    mutate(event0 = ifelse(is.na(event0),0,event0), # replace NA with 0
           event1 = ifelse(is.na(event1),0,event1),
           risk_set = event0 + event1) %>% # define the risk set
    mutate(hazard = (event1 / risk_set) %>% round(digits = 3)) %>% # calculate hazard estimate
    mutate(se_haz = sqrt((hazard * (1 - hazard)) / risk_set) %>% round(digits = 4), # standard error for hazard
           pmass = event1/max(risk_set),
           se_pmass = sqrt((pmass * (1 - pmass)) / max(risk_set))) %>% 
    group_by(condition) %>%
    mutate(survival = (cumprod(1-hazard)) %>% round(digits = 4), # calculate survival estimate
           term     = (cumsum(hazard / (risk_set * (1 - hazard)))) %>% round(digits = 7), # intermediate calculation
           se_surv  = (survival * sqrt(term)) %>% round(digits = 5)  ) %>% # Greenwood's (1926) approximation
    ungroup() 
```

Calaculate conditional accuracy:

```{r}
ca <- data_fig1_hazard %>% 
    filter(event == 1) %>%
    group_by(condition,bin) %>%
    summarize(ca = mean(acc) %>% round(digits = 2),
              n = n(),
              .groups = 'drop') %>%
    ungroup() %>%
    mutate(se_ca = sqrt((ca * (1-ca)) / n) %>% round(digits = 3)) 
ca
```

## 2. Plot hazard and conditional accuracy

```{r}
p13.1 <-ggplot(lifetable_fig1, aes(x = bin, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits = c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
 # ggtitle("hazard and conditional accuracy functions") +
  xlab("time bin endpoint") +
  theme(axis.text.x = element_text(angle = 90))
p13.1

#ggsave("sims/figures/haz_surv_single.jpeg",
#       width = 7, height = 5, dpi=800)
```

```{r}
p13.2 <-ggplot(ca, aes(x = bin, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits=c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("time bin endpoint") +
    ylab("conditional accuracy") +
   theme(axis.text.x = element_text(angle = 90))

 # ggtitle("conditional accuracy functions") 
#+ 
#  guides(color=guide_legend(title="prime type"))
p13.2
```

Combine plots

```{r}
p13.3 <- (p13.1 / p13.2) +
  plot_layout(guides = 'collect',
              axes = 'collect')
p13.3
```

## 3. Create RT data (assuming uniform distribution within a bin) and calculate means

```{r}
rt_dat_fig1 <- data_fig1_hazard %>%
  filter(event==1) %>% 
  mutate(u = bin*100,
         l = u-100,
         m = (l + u)/2) %>% 
  group_by(subj, trial, condition, bin) %>% 
  # mutate(rt = rtruncnorm(n=1, mean=m, sd=25, a=l, b=u))
  mutate(rt = runif(n=1, min=l, max=u))

head(rt_dat_fig1)
summary(rt_dat_fig1)
```

create summary RT data per condition at the pid level for plotting mean comparisons

```{r}
rt_dat_fig1_pid <- rt_dat_fig1 %>%
  group_by(condition) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # 
            sem = (sd/sqrt(n)))
rt_dat_fig1_pid
```

create summary ACC data per condition at the pid level for plotting mean comparisons

```{r}
acc_dat_fig1_pid <- rt_dat_fig1 %>%
  group_by(condition) %>% 
  summarise(mean = mean(acc),
            sd = sd(acc),
            n = n(), # 
            sem = (sd/sqrt(n)))
acc_dat_fig1_pid
```

## 4. plot rt + accuracy

```{r}
p13.4 <- ggplot(rt_dat_fig1_pid, aes(x = condition, y = mean, fill=condition, color=condition)) +
  geom_col(alpha = 0.9, width = 0.6) +
  geom_errorbar(
    aes(ymin = mean - sem, ymax = mean + sem),
    width = 0.2,
    linewidth = 0.8,
    color = "black"
  ) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
 #  ggtitle("mean RT by condition") +
   scale_y_continuous(limits = c(0, 600), breaks = seq(0, 600, 100)) +
   ylab("mean RT (ms)")
p13.4
```

```{r}
p13.5 <- ggplot(acc_dat_fig1_pid, aes(x = condition, y = mean, fill=condition, color=condition)) +
  geom_col(alpha = 0.9, width = 0.6) +
  geom_errorbar(
    aes(ymin = mean - sem, ymax = mean + sem),
    width = 0.2,
    linewidth = 0.8,
    color = "black"
  ) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
 #  ggtitle("mean accuracy by condition") +
   scale_y_continuous(limits = c(0, 1)) +
   ylab("accuracy")
p13.5
```

```{r}
p13.6 <- (p13.4 / p13.5) +
  plot_layout(guides = 'collect',
              axes = 'collect')
p13.6

plot_grid(p13.6, p13.3,
  nrow = 1,
  labels = c("A","B"),
  label_size = 22
)

```{r}
ggsave("sims/figures/Fig1_revision1.jpeg",
       width = 10, height = 10, dpi=800)
